---
title: "Data sets for Introduction to Machine Learning"
subtitle: "Analytics connect '18"
author: "Brandon M. Greenwell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Prerequisites

```{r prerequisites, eval=FALSE}
# Install required packages
install.packages(c("AmesHousing", "kernlab", "pdp"))
```


# Regression

## Boston housing data

Data on median housing values from 506 census tracts in the suburbs of Boston from the 1970 census. This data frame is a corrected version of the original data by [Harrison and Rubinfeld (1978)](https://www.sciencedirect.com/science/article/abs/pii/0095069678900062) with additional spatial information. The data are available in the [pdp](https://cran.r-project.org/package=pdp) package which were taken directly from [mlbench](https://cran.r-project.org/package=mlbench) after the removal of unneeded columns (i.e., name of town, census tract, and the uncorrected median home value). See `?pdp::boston` for details.

```{r boston}
# Load the Boston housing data
data(boston, package = "pdp")

# View the Ames housing data
DT::datatable(boston, extensions = "FixedColumns",
  options = list(
    dom = "t",
    scrollX = TRUE,
    fixedColumns = TRUE
))
```


## Ames housing data

The [AmesHousing](https://cran.r-project.org/package=AmesHousing) package contains a processed version of the data described by [De Cock (2011)](https://ww2.amstat.org/publications/jse/v19n3/decock.pdf) where 82 fields were recorded for 2,930 properties in Ames IA. A description of each field can be found [here](https://www.kaggle.com/c/house-prices-advanced-regression-techniques/data). This is a more contemporary alternative to the Boston housing data described above.

```{r ames}
# Load the Ames housing data
ames <- AmesHousing::make_ames()

# View the Ames housing data
DT::datatable(ames, extensions = "FixedColumns",
  options = list(
    dom = "t",
    scrollX = TRUE,
    fixedColumns = TRUE
))
```


# Classification

## Mushroom edibility

There is no simple rule for determining the edibility of a mushroom; no rules like "leaflets three, let it be", "hairy vine, no friend of mine" and "berries white, run in fright" for poison ivy. The following data, taken from the [UCI Machine Learning Reposirtory](https://archive.ics.uci.edu/ml/datasets/mushroom) contain 21 physical characteristics on 8,124 mushrooms classified as either poisonous or edible.

```{r mushroom}
# Load the mushroom data
mushroom <- read.csv("https://bgreenwell.github.io/MLDay18/data/mushroom.csv")

# View the mushroom data
DT::datatable(mushroom, extensions = "FixedColumns",
  options = list(
    dom = "t",
    scrollX = TRUE,
    fixedColumns = TRUE
))
```


## E-mail spam data

This is a data set collected at Hewlett-Packard Labs, that classifies 4,601 e-mails as spam or non-spam (i.e., "ham"). There are 2,788 non-spam e-mails and 1.813 spam e-mails. In addition to this class label there are 57 variables indicating the frequency of certain words and characters in the e-mail. The first 48 variables contain the frequency of the variable name (e.g., business) in the e-mail. If the variable name starts with "num" (e.g., num650) then it indicates the frequency of the corresponding number (e.g., 650). The variables 49--54 indicate the frequency of the characters ';', '(', '[', '!', '\$', and '\#'. The variables 55--57 contain the average, longest and total run-length of capital letters. Variable 58 indicates the type of the mail and is either "nonspam" or "spam", i.e. unsolicited commercial e-mail. See `?kernlab::spam` for details.

The "spam" concept is diverse: advertisements for products/web sites, make money fast schemes, chain letters, pornography, etc. This collection of spam e-mails came from the collectors' postmaster and individuals who had filed spam. The collection of non-spam e-mails came from filed work and personal e-mails, and hence the word 'george' and the area code '650' are indicators of non-spam. These are useful when constructing a personalized spam filter. One would either have to blind such non-spam indicators or get a very wide collection of non-spam to generate a general purpose spam filter.

```{r spam}
# Load the email spam data
data(spam, package = "kernlab")

# View the email spam data
DT::datatable(spam, extensions = "FixedColumns",
  options = list(
    dom = "t",
    scrollX = TRUE,
    fixedColumns = TRUE
))
```