---
title: "Data sets for Introduction to Machine Learning"
subtitle: "Analytics connect '18"
author: "Brandon M. Greenwell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Ames housing data

The [AmesHousing](https://cran.r-project.org/package=AmesHousing) package contains a processed version of the data described by [De Cock (2011)](https://ww2.amstat.org/publications/jse/v19n3/decock.pdf) where 82 fields were recored for 2,930 properties in Ames IA. A description of each field can be found [here](https://www.kaggle.com/c/house-prices-advanced-regression-techniques/data).

```{r ames-housing}
# Load the Ames housing data
ames <- AmesHousing::make_ames()

# View the Ames housing data
# DT::datatable(ames[1:10, ], extensions = "FixedColumns",
#   options = list(
#     dom = "t",
#     scrollX = TRUE,
#     fixedColumns = TRUE
# ))  
```


# E-mail spam data

This is a data set collected at Hewlett-Packard Labs, that classifies 4,601 e-mails as spam or non-spam (i.e., "ham"). There are 2,788 non-spam e-mails and 1.813 spam e-mails. In addition to this class label there are 57 variables indicating the frequency of certain words and characters in the e-mail. The first 48 variables contain the frequency of the variable name (e.g., business) in the e-mail. If the variable name starts with "num" (e.g., num650) then it indicates the frequency of the corresponding number (e.g., 650). The variables 49--54 indicate the frequency of the characters ';', '(', '[', '!', '\$', and '\#'. The variables 55--57 contain the average, longest and total run-length of capital letters. Variable 58 indicates the type of the mail and is either "nonspam" or "spam", i.e. unsolicited commercial e-mail. See `?kernlab::spam` for details.

The "spam" concept is diverse: advertisements for products/web sites, make money fast schemes, chain letters, pornography, etc. This collection of spam e-mails came from the collectors' postmaster and individuals who had filed spam. The collection of non-spam e-mails came from filed work and personal e-mails, and hence the word 'george' and the area code '650' are indicators of non-spam. These are useful when constructing a personalized spam filter. One would either have to blind such non-spam indicators or get a very wide collection of non-spam to generate a general purpose spam filter.

```{r e-mail-spam}
# Load the email spam data
data(spam, package = "kernlab")

# View the email spam data
# DT::datatable(spam[1:10, ], extensions = "FixedColumns",
#   options = list(
#     dom = "t",
#     scrollX = TRUE,
#     fixedColumns = TRUE
# )) 
```